\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage[a4paper, margin=1.5in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{array}

\renewcommand{\arraystretch}{1.5}

\title{Task 2 Report}
\date{\today}
\author{Federico Fregosi, Mirko Laruina,\\
        Riccardo Mancini, Gianmarco Petrelli}

\begin{document}
\pagenumbering{gobble}
\maketitle
\vfill
% \setcounter{tocdepth}{1}
\tableofcontents
\vfill
\clearpage
\setcounter{page}{1}
\pagenumbering{arabic}

\section{Specifications}

\subsection{Application Overview}
The application is an aggregator of movie and movie's ratings with the purpose 
of providing logged users statistics and informations about a large set of movies.
Logged-in user can also rate movies they have watched while not logged-in users 
may still use the service to browse movie rankings and statistics but they are not
able to give their rate. Only movies released in Italy are considered.

All users can search a movie and view its details (e.g., title, original title, duration, 
cast, ...) along with its aggregated statistics about ratings. 

In addition, all users can browse movie lists such as:
\begin{itemize}
    \item alphabetic list of movies
    \item rankings based on ratings
    \item last added movies
\end{itemize} 

Over these lists the user can apply filters based on, for example, genre, 
year, casting, etc.

System administrators can check all accounts and ban users.

The movie database will be built upon the publicly available IMDb dataset.

The ratings will be gathered also by periodically scraping other websites 
(e.g., Rotten Tomatoes, Coming Soon, MyMovies).

\subsection{Actors}
Anonymous user, registered user, administrator and bot.

\subsection{Requirement Analysis}

\subsubsection{Functional Requirements}
An \textbf{anonymous user} must be able to register in order to become a 
\textit{registered user}. Login is carried out using username and password selected 
by the user when registering. Username must be unique. A valid email address is
also required in order to register. An email cannot be used more than once.

Both \textbf{anonymous user} and \textbf{registered user} must be able to:
\begin{itemize}
	\item check informations and average rating of a specific movie
	\item check a movie's list and filter it by many characteristics. Combined filters 
	are also allowed.
	\item check aggregated statistics about movie grouped by year, country, actor,
	director, genre 
\end{itemize}

A \textbf{registered user} must be able to rate a movie, in addition to what anonymous
user can do. A registered user must also be able to manage his profile. In the profile a
registered user can:
\begin{itemize}
	\item check, add and modify his personal data
	\item browse the history of his rates
	\item view aggregated statistics about his profile (i.e. most viewed genre,
	most recurrent actor, etc...) based on his rated movies
	\item delete the account
\end{itemize}
Finally, a registered user can logout in any moment.

An \textbf{administrator} is a special registered user who must be able to ban users.
In order to do that, an administrator can check a global rating history to retrieve informations
about all the application's activity, and to check every user's profile.
Banned user's rating are automatically removed from the database. Email and username
of banned users cannot be used again.

The \textbf{bot} is not a real user but an entity used to update the database if a 
new film needs to be added. Moreover, the bot periodically browses all the source sites from 
where ratings are collected in order to find new ratings and add them to our 
application's database.

\subsubsection{Non-Functional Requirements}
\begin{itemize}
	\item Availability: the Database must be replicated in order to be always available.
	Write operations on the Database can be eventually consistent.
	\item Scalability: the application must be able to scale to an arbitrary number of servers.
	\item Security: passwards must be stored in a secure way.
	\item Responsive UI: Client-side application must provide a responsive view both for pc, 
	laptops and mobile devices.
\end{itemize}

\section{Design}

\subsection{Use-case diagram}

\subsection{Class diagram}

\subsection{Data model}

\subsection{Software Architecture}

%DUBBI
%username must be unique? (functional or not functional?)
%->unique, functional, inserire anche in task 1
%the only difference between anonymous and registered user is that reg. user can rate?
%->+profile with stats on him
%can a film be marked as watched?
%->no
%email is necessary for registration?
%->yes + personal informations (not required)

\end{document}
